\hspace{-0.1cm}{J-ReCoVer}:~Java~Reducer~Commutativity~Verifier

### 2019-06-25 draft.tex
sec 4

After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
never calls the $\cur$ function in the $s_1$ part before entering the loop.
Further, we assume w.l.o.g. that the reducer reads exactly one input in one loop
iteration. When multiple reads from the input occur in a single branch of the
loop, we can use additional variables and break the branch into several
auxiliary ones, each reading just once.

>>>>

After the transformation described above, the reducer $s_1;\rloop\{s_2\};s_3$
never calls the $\cur$ function in the $s_1$ part before entering the loop.
Further, we assume w.l.o.g. that the reducer reads exactly one input in one loop
iteration. When multiple reads from the input occur in a single execution path from the begin to the end of
the loop body, we can use additional variables and branch statements to break the path into several
auxiliary ones, each reading just once.
